Design, Implementation, and Evaluation of Open Power Quality

### 2020-07-31 manuscript.v5/energies-864131.tex
checkpoint

%=================================================================
% Full title of the paper (Capitalized)
\Title{%The paper was slightly modified by our English editor, please check the whole text and confirm if your meaning is retained; 2.	Do not delete any comment we left for you and reply to each comment so that we can understand your meaning clearly; 3.	If you need to revise somewhere in your paper, please highlight the revisions to let us know. (Thank you for your cooperation in advance.)
\highlight{Design}, Implementation, and Evaluation of Open Power Quality}

% Authors, for the paper (add full first names)
\Author{\hl{Anthony} %Please carefully check the accuracy of names and affiliations. 
J. Christe, Sergey Negrashov and Philip M. Johnson *}

@@

%%% We added a space between 5 and V. Please confirm.

@@

\highlight{{\em IEEE 1159 Voltage Actor.}} The IEEE 1159 Voltage Actor is used to classify voltage Incidents in accordance with the IEEE 1159 standard \hl{[29]}. In~general, this standard classifies voltage disturbances by duration and by magnitude. Voltage durations are classified from 0.5 to 30 cycles, 30 cycles to 3~s, 3 s to a minute, and~greater than 1 minute. Voltage deviations are classified in both the sag and swell directions as a percentage from nominal. Sags are generally classified between 10\% and 90\% of nominal while swells are generally classified from 110\% to 180\% of nominal. This Actor is capable of classifying voltage sags, swells, and~interruptions as defined by the standard, and~creating data at the Incident Layer if~appropriate.
%%% Should it be reference citation? 
\highlight{{\em Box Optimization Actor.}} The Box Optimization Actor is responsible for sending and receiving typed messages to and from OPQ Boxes from OPQ Mauka. This Actor is capable of requesting the state of each OPQ Box (e.g., uptime, Measurement rate, security keys). It is also capable of adjusting the state of individual OPQ Boxes by changing things such as the Measurement and Trend rate or the sampling rate used by the~Box.

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.4\linewidth]{images/pilot/data-management-graph.png}
\caption{\hl{Storage} requirements with and without~time-to-live (TTL).} %%% It seems that the figure isn't complete, please modify.
\label{fig:data-management-graph}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{\hl{For} }%% research articles with several authors, a short paragraph specifying their individual contributions must be provided. The following statements should be used ``Conceptualization, X.X. and Y.Y.; methodology, X.X.; software, X.X.; validation, X.X., Y.Y. and Z.Z.; formal analysis, X.X.; investigation, X.X.; resources, X.X.; data curation, X.X.; writing--original draft preparation, X.X.; writing--review and editing, X.X.; visualization, X.X.; supervision, X.X.; project administration, X.X.; funding acquisition, Y.Y. All authors have read and agreed to the published version of the manuscript.'', please turn to the  \href{http://img.mdpi.org/data/contributor-role-instruction.pdf}{CRediT taxonomy} for the term explanation. Authorship must be limited to those who have contributed substantially to the work reported.

@@

@@

@@

\bibitem[Trabish(2014)]{trabish_solar_2014}
Trabish, H.
\newblock Solar Installers flee {Hawaii} as Interconnection Queue Backs Up.
\newblock {\em Utility Dive}, {\hl{2014}}.%% Please add day month.

@@

\bibitem[Anurangi \em{et~al.}(2017)Anurangi, Rodrigo, and
Jayatunga]{anurangi_effects_2017}
Anurangi, R.O.; Rodrigo, A.S.; Jayatunga, U.
\newblock Effects of high levels of harmonic penetration in distribution
networks with photovoltaic inverters.
\newblock In {Proceedings of the } 2017 {IEEE} {International} {Conference} on IEEE Industrial and {Information} {Systems} ({ICIIS}),  \hl{2017}; pp. 1--6, doi:10.1109/ICIINFS.2017.8300335.%% Please add conference location and date.

@@

\bibitem[Delgado \em{et~al.}(2011)Delgado, Santos, de~Almeida, and
Figueira]{delgado_solutions_2011}
Delgado, J.; Santos, B.; de~Almeida, A.T.; Figueira, A.
\newblock Solutions to mitigate power quality disturbances resulting from
integrating intermittent renewable energy in the grid of {Porto} {Santo}.
\newblock In {Proceedings of the } 11th {International} {Conference} on {Electrical} {Power} {Quality}
and {Utilisation}, \hl{2011}; pp. 1--6, 
\newblock ISSN 2150-6655,
doi:{\changeurlcolor{black}\href{https://doi.org/10.1109/EPQU.2011.6128870}{\detokenize{10.1109/EPQU.2011.6128870}}}.

\bibitem[Zavoda(2018)]{zavoda_power_2018}
Zavoda, F.
\newblock { Power {Quality} and {EMC} {Issues} with {Future} {Electricity}
{Networks}}. In {Proceedings of the } CIGRE, \hl{2018}.

\bibitem[Nakafuji \em{et~al.}(2011)Nakafuji, Aukai, Dangelmaier, Reynolds,
Yoshimura, and {Ying Hu}]{nakafuji_back--basics_2011}
Nakafuji, D.; Aukai, T.; Dangelmaier, L.; Reynolds, C.; Yoshimura, J.; {
Hu, Y}.
\newblock “{Back}-to-basics”: {Operationalizing} data mining and visualization
techniques for utilities.
\newblock In {Proceedings of the }The 2011 International Joint Conference on Neural Networks, \hl{2011}; pp. 3093--3098, doi:10.1109/IJCNN.2011.6033630.

\bibitem[Dedad(2008)]{dedad_when_2008}
Dedad, J.
\newblock When {Does} {Poor} {Power} {Quality} {Cause} {Electronics}
{Failures}?
\newblock {\em Electrical Construction and Maintenance Magazine}, {\hl{2008}}.
\newblock Library Catalog.  Available online:  \url{www.ecmweb.com} (accessed on \hl{day month year}).

\bibitem[Elphick \em{et~al.}(2015)Elphick, Ciufo, Smith, and
Parera]{elphick_summary_2015}
Elphick, S.; Ciufo, P.; Smith, V.; Parera, S.
\newblock Summary of the economic impacts of power quality on consumers.
\newblock  In {Proceedings of the }2015 {Australasian} {Universities} {Power} {Engineering}
{Conference}, \hl{2015}.

\bibitem[Laskar(2012)]{laskar_power_2012}
Laskar, S.H.
\newblock Power quality issues and need of intelligent {PQ} monitoring in the
smart grid environment.
\newblock In~{Proceedings of the }2012 47th
{International} Universities {Power} {Engineering} {Conference} ({UPEC}), \hl{2012}; pp.~1--6.

\bibitem[Negrashov(2020)]{negrashov_opq_2020}
Negrashov, S.
\newblock {OPQ} {Box} {Specifications} and {Design}, 2020.
\newblock Library Catalog.  Available online:  \url{github.com} (accessed on \hl{day month year}).

\bibitem[Unruh(2018)]{unruh_ieee_2018}
Unruh, T.
\newblock \emph{IEEE P1159/D3: {Draft} {Recommended} {Practice} for
{Monitoring} {Electric} {Power} {Quality}}; \hl{2018}. %% Please provide publisher and its location.

@@

\bibitem[Thallam and Heydt(2000)]{thallam_power_2000}
Thallam, R.; Heydt, G.
\newblock Power acceptability and voltage sag indices in the three phase sense.
\newblock In {Proceedings of the } 2000 {Power} {Engineering} {Society} {Summer} {Meeting}, 
 \hl{2000}; Volume~2, pp. 905--910, doi:10.1109/PESS.2000.867482.

@@

\bibitem[Dickens \em{et~al.}(2019)Dickens, Christe, and
Johnson]{dickens_transient_2019}
Dickens, C.; Christe, A.; Johnson, P.
\newblock A {Transient} {Classification} {System} {Implementation} on an {Open}
{Source} {Distributed} {Power} {Quality} {Network}.
\newblock  In Proceedings of the {Ninth} {International} {Conference} on {Smart}
{Grids}, {Green} {Communications} and {IT} {Energy}-aware {Technologies},
\hl{2019}.

\bibitem[Fluke(2020)]{fluke_fluke_2020}
Fluke, I.
\newblock \emph{Fluke {Corporation}: {Fluke} {Electronics}, {Biomedical},
{Calibration} and {Networks}}; \hl{2020}.

\bibitem[Dranetz(2020)]{dranetz_dranetz_2020}
Dranetz, I.
\newblock Dranetz {Power} {Monitoring}, 2020.
\newblock Library Catalog. Available online:  \url{ www.dranetz.com} (accessed on \hl{day month year}).

\bibitem[Elspec(2020)]{elspec_elspec_2020}
Elspec, I.
\newblock Elspec---{Power} Quality Analyzers and Solutions, 2020.
\newblock Library Catalog. Available online:  \url{www.elspec-ltd.com} (accessed on \hl{day month year}).

\bibitem[Powerside(2020)]{powerside_powerside_2020}
Powerside, I.
\newblock Powerside, {Inc}., 2020.
\newblock Library Catalog. Available online:  \url{Powerside.com}  (accessed on \hl{day month year}).

\bibitem[ACR(2020)]{acr_acr_2020}
ACR, S.
\newblock {ACR} {Systems}, 2020.
\newblock Library Catalog. Available online:  \url{www.acrdatasolutions.com}  (accessed on \hl{day month year}).

@@

\bibitem[Concepts(2020)]{electrotek_concepts_pqview_2020}
Concepts, E.
\newblock {PQView} 4 {\textbar} {Electrotek} {Concepts}, 2020.
\newblock Library Catalog. Available online:  \url{www.electrotek.com}  (accessed on \hl{day month year}).

\bibitem[{Elspec, Ltd}(2016)]{elspec_ltd_pqscada_2016}
{Elspec, Ltd}.
\newblock {PQSCADA} {Sapphire}, 2016.
\newblock Library Catalog. Available online:  \url{www.elspec-ltd.com}  (accessed on \hl{day month year}).

\bibitem[Sabin(2020)]{sabin_ieee_2020}
Sabin, D.
\newblock \emph{{IEEE} 1159.3 {PQDIF} {Task} {Force}}; \hl{2020}.

\bibitem[Alliance(2020)]{grid_protection_alliance_grid_2020}
Alliance, G.P.
\newblock \emph{Grid {Protection} {Alliance}---{Home}}; \hl{2020}.

\bibitem[Di~Manno \em{et~al.}(2015)Di~Manno, Varalone, Verde, De~Santis,
Di~Perna, and Salemme]{di_manno_user_2015}
Di~Manno, M.; Varalone, P.; Verde, P.; De~Santis, M.; Di~Perna, C.; Salemme, M.
\newblock User friendly smart distributed measurement system for monitoring and
assessing the electrical power quality.
\newblock In Proceedings of the 2015 {AEIT} {International} {Annual}
{Conference}, \hl{2015}.

\bibitem[Daponte \em{et~al.}(2000)Daponte, Di~Penta, and
Mercurio]{daponte_transientmeter:_2000}
Daponte, P.; Di~Penta, M.; Mercurio, G.
\newblock {TRANSIENTMETER}: A distributed measurement system for power quality
monitoring.
\newblock In {Proceedings of the } Ninth {International} {Conference} on {Harmonics} and {Quality} of
{Power}, \hl{2000}.

>>>>

%=================================================================
% Full title of the paper (Capitalized)
\Title{%The paper was slightly modified by our English editor, please check the whole text and confirm if your meaning is retained; 2.	Do not delete any comment we left for you and reply to each comment so that we can understand your meaning clearly; 3.	If you need to revise somewhere in your paper, please highlight the revisions to let us know. (Thank you for your cooperation in advance.)  (CONFIRMED)
\highlight{Design}, Implementation, and Evaluation of Open Power Quality}

% Authors, for the paper (add full first names)
\Author{\hl{Anthony} %Please carefully check the accuracy of names and affiliations. (CONFIRMED)
J. Christe, Sergey Negrashov and Philip M. Johnson *}

@@

%%% We added a space between 5 and V. Please confirm. CONFIRMED.

@@

\highlight{{\em IEEE 1159 Voltage Actor.}} The IEEE 1159 Voltage Actor is used to classify voltage Incidents in accordance with the IEEE 1159 standard \hl{[29]}. In~general, this standard classifies voltage disturbances by duration and by magnitude. Voltage durations are classified from 0.5 to 30 cycles, 30 cycles to 3~s, 3 s to a minute, and~greater than 1 minute. Voltage deviations are classified in both the sag and swell directions as a percentage from nominal. Sags are generally classified between 10\% and 90\% of nominal while swells are generally classified from 110\% to 180\% of nominal. This Actor is capable of classifying voltage sags, swells, and~interruptions as defined by the standard, and~creating data at the Incident Layer if~appropriate.
%%% Should it be reference citation? YES
\highlight{{\em Box Optimization Actor.}} The Box Optimization Actor is responsible for sending and receiving typed messages to and from OPQ Boxes from OPQ Mauka. This Actor is capable of requesting the state of each OPQ Box (e.g., uptime, Measurement rate, security keys). It is also capable of adjusting the state of individual OPQ Boxes by changing things such as the Measurement and Trend rate or the sampling rate used by the~Box.

@@

\begin{figure}[H]
\centering
\includegraphics[width=0.4\linewidth]{images/pilot/data-management-graph.png}
\caption{\hl{Storage} requirements with and without~time-to-live (TTL).} %%% It seems that the figure isn't complete, please modify. FIGURE IS COMPLETE.
\label{fig:data-management-graph}
\end{figure}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\authorcontributions{\hl{For} }%% research articles with several authors, a short paragraph specifying their individual contributions must be provided. The following statements should be used ``Conceptualization, X.X. and Y.Y.; methodology, X.X.; software, X.X.; validation, X.X., Y.Y. and Z.Z.; formal analysis, X.X.; investigation, X.X.; resources, X.X.; data curation, X.X.; writing--original draft preparation, X.X.; writing--review and editing, X.X.; visualization, X.X.; supervision, X.X.; project administration, X.X.; funding acquisition, Y.Y. All authors have read and agreed to the published version of the manuscript.'', please turn to the  \href{http://img.mdpi.org/data/contributor-role-instruction.pdf}{CRediT taxonomy} for the term explanation. Authorship must be limited to those who have contributed substantially to the work reported. SEE BELOW

\authorcontributions{
Conceptualization, Johnson, Christe, Negrashov; methodology, Johnson, Christe, Negrashov; software, Johnson, Christe, Negrashov; validation, Johnson, Christe, Negrashov; formal analysis, Johnson, Christe, Negrashov; investigation, Johnson, Christe, Negrashov; resources, Johnson; data curation, Christe, Negrashov; writing--original draft preparation, Johnson, Christe, Negrashov; writing--review and editing, Johnson, Christe, Negrashov; visualization, Johnson, Christe, Negrashov; supervision, Johnson; project administration, Johnson; funding acquisition, Johnson. All authors have read and agreed to the published version of the manuscript.
}

@@

\funding{This research was funded in part by a grant from the University of Hawaii President's Green Award program.}

@@

\conflictsofinterest{The authors declare no conflict of interest.}

@@

\bibitem[Trabish(2014)]{trabish_solar_2014}
Trabish, H.
\newblock Solar Installers flee {Hawaii} as Interconnection Queue Backs Up.
\newblock {\em Utility Dive}, {\hl{September 29, 2014}}.%% Please add day month. DONE

@@

\bibitem[Anurangi \em{et~al.}(2017)Anurangi, Rodrigo, and
Jayatunga]{anurangi_effects_2017}
Anurangi, R.O.; Rodrigo, A.S.; Jayatunga, U.
\newblock Effects of high levels of harmonic penetration in distribution
networks with photovoltaic inverters.
\newblock In {Proceedings of the } 2017 {IEEE} {International} {Conference} on IEEE Industrial and {Information} {Systems} ({ICIIS}), Jayapura, Indonesia \hl{November 2, 2017}; pp. 1--6, doi:10.1109/ICIINFS.2017.8300335.%% Please add conference location and date.

@@

\bibitem[Delgado \em{et~al.}(2011)Delgado, Santos, de~Almeida, and
Figueira]{delgado_solutions_2011}
Delgado, J.; Santos, B.; de~Almeida, A.T.; Figueira, A.
\newblock Solutions to mitigate power quality disturbances resulting from
integrating intermittent renewable energy in the grid of {Porto} {Santo}.
\newblock In {Proceedings of the } 11th {International} {Conference} on {Electrical} {Power} {Quality}
and {Utilisation}, \hl{October 17, 2011}; pp. 1--6,
\newblock ISSN 2150-6655,
doi:{\changeurlcolor{black}\href{https://doi.org/10.1109/EPQU.2011.6128870}{\detokenize{10.1109/EPQU.2011.6128870}}}.

\bibitem[Zavoda(2018)]{zavoda_power_2018}
Zavoda, F.
\newblock { Power {Quality} and {EMC} {Issues} with {Future} {Electricity}
{Networks}}. In {Proceedings of the } CIGRE, \hl{May 15, 2018}.

\bibitem[Nakafuji \em{et~al.}(2011)Nakafuji, Aukai, Dangelmaier, Reynolds,
Yoshimura, and {Ying Hu}]{nakafuji_back--basics_2011}
Nakafuji, D.; Aukai, T.; Dangelmaier, L.; Reynolds, C.; Yoshimura, J.; {
Hu, Y}.
\newblock “{Back}-to-basics”: {Operationalizing} data mining and visualization
techniques for utilities.
\newblock In {Proceedings of the }The 2011 International Joint Conference on Neural Networks, \hl{July 31, 2011}; pp. 3093--3098, doi:10.1109/IJCNN.2011.6033630.

\bibitem[Dedad(2008)]{dedad_when_2008}
Dedad, J.
\newblock When {Does} {Poor} {Power} {Quality} {Cause} {Electronics}
{Failures}?
\newblock {\em Electrical Construction and Maintenance Magazine}, {\hl{November 1, 2008}}.
\newblock Library Catalog.  Available online:  \url{www.ecmweb.com} (accessed on \hl{31 July 2020}).

\bibitem[Elphick \em{et~al.}(2015)Elphick, Ciufo, Smith, and
Parera]{elphick_summary_2015}
Elphick, S.; Ciufo, P.; Smith, V.; Parera, S.
\newblock Summary of the economic impacts of power quality on consumers.
\newblock  In {Proceedings of the }2015 {Australasian} {Universities} {Power} {Engineering}
{Conference}, \hl{September 27, 2015}.

\bibitem[Laskar(2012)]{laskar_power_2012}
Laskar, S.H.
\newblock Power quality issues and need of intelligent {PQ} monitoring in the
smart grid environment.
\newblock In~{Proceedings of the }2012 47th
{International} Universities {Power} {Engineering} {Conference} ({UPEC}), \hl{September 4, 2012}; pp.~1--6.

\bibitem[Negrashov(2020)]{negrashov_opq_2020}
Negrashov, S.
\newblock {OPQ} {Box} {Specifications} and {Design}, 2020.
\newblock Library Catalog.  Available online:  \url{github.com} (accessed on \hl{31 July 2020}).

\bibitem[Unruh(2018)]{unruh_ieee_2018}
Unruh, T.
\newblock \emph{IEEE P1159/D3: {Draft} {Recommended} {Practice} for
{Monitoring} {Electric} {Power} {Quality}}; IEEE, New York, NY \hl{February 1, 2018}. %% Please provide publisher and its location. DONE

@@

\bibitem[Thallam and Heydt(2000)]{thallam_power_2000}
Thallam, R.; Heydt, G.
\newblock Power acceptability and voltage sag indices in the three phase sense.
\newblock In {Proceedings of the } 2000 {Power} {Engineering} {Society} {Summer} {Meeting},
 \hl{July 16, 2000}; Volume~2, pp. 905--910, doi:10.1109/PESS.2000.867482.

@@

\bibitem[Dickens \em{et~al.}(2019)Dickens, Christe, and
Johnson]{dickens_transient_2019}
Dickens, C.; Christe, A.; Johnson, P.
\newblock A {Transient} {Classification} {System} {Implementation} on an {Open}
{Source} {Distributed} {Power} {Quality} {Network}.
\newblock  In Proceedings of the {Ninth} {International} {Conference} on {Smart}
{Grids}, {Green} {Communications} and {IT} {Energy}-aware {Technologies},
\hl{June 2, 2019}.

\bibitem[Fluke(2020)]{fluke_fluke_2020}
Fluke, I.
\newblock \emph{Fluke {Corporation}: {Fluke} {Electronics}, {Biomedical},
{Calibration} and {Networks}}; \hl{July 31, 2020}.

\bibitem[Dranetz(2020)]{dranetz_dranetz_2020}
Dranetz, I.
\newblock Dranetz {Power} {Monitoring}, 2020.
\newblock Library Catalog. Available online:  \url{ www.dranetz.com} (accessed on \hl{31 July 2020}).

\bibitem[Elspec(2020)]{elspec_elspec_2020}
Elspec, I.
\newblock Elspec---{Power} Quality Analyzers and Solutions, 2020.
\newblock Library Catalog. Available online:  \url{www.elspec-ltd.com} (accessed on \hl{31 July 2020}).

\bibitem[Powerside(2020)]{powerside_powerside_2020}
Powerside, I.
\newblock Powerside, {Inc}., 2020.
\newblock Library Catalog. Available online:  \url{Powerside.com}  (accessed on \hl{31 July 2020}).

\bibitem[ACR(2020)]{acr_acr_2020}
ACR, S.
\newblock {ACR} {Systems}, 2020.
\newblock Library Catalog. Available online:  \url{www.acrdatasolutions.com}  (accessed on \hl{31 July 2020}).

@@

\bibitem[Concepts(2020)]{electrotek_concepts_pqview_2020}
Concepts, E.
\newblock {PQView} 4 {\textbar} {Electrotek} {Concepts}, 2020.
\newblock Library Catalog. Available online:  \url{www.electrotek.com}  (accessed on \hl{31 July 2020}).

\bibitem[{Elspec, Ltd}(2016)]{elspec_ltd_pqscada_2016}
{Elspec, Ltd}.
\newblock {PQSCADA} {Sapphire}, 2016.
\newblock Library Catalog. Available online:  \url{www.elspec-ltd.com}  (accessed on \hl{31 July 2020}).

\bibitem[Sabin(2020)]{sabin_ieee_2020}
Sabin, D.
\newblock \emph{{IEEE} 1159.3 {PQDIF} {Task} {Force}}; \hl{July 31, 2020}.

\bibitem[Alliance(2020)]{grid_protection_alliance_grid_2020}
Alliance, G.P.
\newblock \emph{Grid {Protection} {Alliance}---{Home}}; \hl{July 31, 2020}.

\bibitem[Di~Manno \em{et~al.}(2015)Di~Manno, Varalone, Verde, De~Santis,
Di~Perna, and Salemme]{di_manno_user_2015}
Di~Manno, M.; Varalone, P.; Verde, P.; De~Santis, M.; Di~Perna, C.; Salemme, M.
\newblock User friendly smart distributed measurement system for monitoring and
assessing the electrical power quality.
\newblock In Proceedings of the 2015 {AEIT} {International} {Annual}
{Conference}, \hl{October 14, 2015}.

\bibitem[Daponte \em{et~al.}(2000)Daponte, Di~Penta, and
Mercurio]{daponte_transientmeter:_2000}
Daponte, P.; Di~Penta, M.; Mercurio, G.
\newblock {TRANSIENTMETER}: A distributed measurement system for power quality
monitoring.
\newblock In {Proceedings of the } Ninth {International} {Conference} on {Harmonics} and {Quality} of
{Power}, Orlando, Florida \hl{October 1, 2000}.
